---
title: "ANLY 530 Group Assignment (Laboratory 3: Mixed Methods or Semi-Supervised Learning)"
author:
- "Josseline Betio"
- "Akpany Benjamin Ebby"
- "Yajun Wang"
- "Salah Eddine MIFDAL"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
---

---

#### Document as of `r Sys.Date()`

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY530_Laboratory3_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(kableExtra)
read_chunk('R/ANLY530_Laboratory3_Chunks.R')

```

Some helper functions do exists to support the code snippets below such as: ```fullFilePath```

---

```{r loadLibraries, message=FALSE, warning=FALSE}
```

## Collecting the data

Let us start by [Loading the Data Sheets]

```{r loadSheets, message=FALSE, warning=FALSE}
```

# Part 2:
-------------

## Wine Data:

```{r partWineDataPrep, message=FALSE, warning=FALSE}
```

```{r part2Wine, message=FALSE, warning=FALSE}
```

## Analysis

In this part, we did an K-means analysis on the UCI wine dataset. We defined a wssplot function to calculate and plot the within-group sum of squares from k=2 to k=15 clusters. We used the NbClust package to evaluate the kmean results from k=2 to k=15, and it returned with the suggestion that k=3 gained the most of the points from all the criteria. Thus, we chose k=3 as the number of clusters, and fit the data. The resulting cluster sizes are 100 for cluster 1, 
